---
title: "Figure04"
author: "Greg Nishihara"
date: "12/1/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The response of the growth rate to temperature in laboratory culture


The relative growth rate (RGR) was derived from a 6-day culture experiment under an irradiance of 50 µmol photons m^-2^ s^-1^.
The photoperiod was 12L:12D and the experiment was conducted at ten temperature treatments (4, 8, 12, 16, 20, 24, 28, 32, 36, and 40°C).
The culture media used was 1/2 concentration of PES and each individual was cultured in a 300 mL flask. 
Three (n = 3) individuals per temperature level were assigned haphazardly.
The cultures were maintained in a Multi Thermo Incubator (MTI-201, EYELA, Tokyo Rikakikai Co., Ltd., Tokyo, Japan). 
The RGR was quantified using the change in wet weight between days 0 and 6 on a log scale.  

$$
RGR = \frac{\log_{e}(m_f) - \log_{e}(m_i)}{\Delta t}
$$
where $\Delta t$ is the duration of the experiment and $m_f$ and $m_i$ are the final and initial wet weight of the individuals, respectively. 


## Modeling the response of RGR, gross photosynthesis rates, and $\Delta F/Fm'$ to temperature

A Bayesian approach was used to analyze the response of photosynthesis to temperature.
A thermodynamic non-linear model was used to model the temperature response of RGR,
gross photosynthesis rates, and $\Delta F/Fm'$, assuming that physiological rates
enters a less active state above some optimal temperature (Thornley and Johnson 2000; Alexandrov and Yamagata 2007).

$$
y = \frac{y_{max} H_d \exp\left(\frac{H_a}{R \left(K_{opt} - K\right)}\right)}{H_d - H_a \left(1-\exp\left(\frac{H_d}{R \left(K_{opt} - K\right)}\right)\right)} + Z
$$
In this equation, $y$ is the response variable, which is either the relative growth rate, the gross photosynthetic rate, 
or the effective quantum yield ($\Delta F / Fm'$). 
The temperature scale is Kelvin (K). 
The model has four parameters: 
$y_{max}$ scales the model to the range of $y$. 
$K_{opt}$ is the absolute temperature where $y$ is maximized, 
$H_{a}$ is the activation energy in kJ mol^-1^ and 
$H_{d}$ is the deactivation energy in kJ mol^-1^. 
$R$ in this model is the ideal gas constant and has a value of 8.314 J mol^-1^. 
However, an offset $Z$ was added only to the RGR analysis to account for negative growth rates.

In the case of gross photosynthesis rate, the rate was assumed to be a hidden state.
Therefore the gross photosynthesis rate was estimated by simultaneously fitting the measured respiration rates to the Arrhenius equation,
and the observed net photosynthetic rates to the difference between thermodynamic non-linear model and the Arrhenius equation. 

$$
R_d = R_{24} \exp\left(\frac{-E_a}{R}\left(\frac{1}{K - 297.15}\right)\right)
$$
In the light, both photorespiration and non-photorespiratory (i.e., mitochondrial) reactions result in oxygen consumption (Tcherkez et al. 2008); 
however, it is not uncommon for the differences between respiration rates under light and dark conditions to be insignificant (Bellasio et al. 2014). 
Hence, photorespiration was assumed to be adequately described by the dark respiration rate. 
$R_{24}$ is the respiration rate at 24°C and $E_a$ is the activation energy. 
The constant 297.15 is 24°C scaled in absolute temperature. 


## Statistical analysis

Statistical analyses of all the models were conducted using R version 4.0.3 (R Core Team 2020), 
and model fitting was done using the package brms version 2.14.0 (Bürkner 2018). 
The parameters were determined by fitting the relevant models using Bayesian methods. 
The package bmrs using RStan (Stan Development Team 2020) as the backend to sample from the posterior distributions of the parameters, 
and four chains of at least 2,000 samples per chain were generated and assessed for convergence.
Typically, at least 1,000 samples of the parameters of interest are generated. 
Informative normal priors were placed on all parameters of the model by using values from a previous study (Kokubu et al. 2015), and a half-Cauchy prior distribution was placed on the scale parameter of the models (Gelman 2004, 2006).
The error distribution for the RGR and gross photosynthesis rate analysis was the gaussian distribution, and a
beta distribution was used for the analysis of the effective quantum yield.

## Run R


```{r, eval = FALSE, message=FALSE}
source("Figure04.R")
```

```{r, echo = FALSE, message=FALSE}
source("Figure04.R")
```


## The figure

The filenames of the image are `r str_replace(filename, "tex", "pdf")` and `r str_replace(filename, "tex", "png")`.

```{r, fig.cap=CAP}
CAP = "The response of relative growth rates to temperature. The solid line indicates the expected value calculated from the model and
the shaded region indicates the 95% prediction interval of the model. Data are indicated by symbols."

knitr::include_graphics(str_replace(filename, "tex", "png"))
```


```{r, echo = FALSE}
X = data %>% group_by(temperature) %>% 
  summarise(m = mean(value),
            sd = sd(value),
            se = sd(value) / sqrt(length(value) -1))

gen = function(x,y) {
  
}

gen2 = function(x,y, s) {
  z = x %>% filter(str_detect(key, y))
  sprintf("%2.3f (%2.3f to %2.3f) %s", z$value, z$.lower, z$.upper, s)
}
datatable %>% gen2("CT", "°C")
```


## Results

The measured relative growth rates steadily increased from `r gen(X, 4)` at 4°C to a high of 
`r gen(X, 28)` at 28°C, before decreasing to `r gen(X, 32)` at 32°C (mean ± standard deviation).

The model analysis indicated that peak model RGR occurred at `r gen2(datatable, "CT", "°C")`
and was `r gen2(datatable, "PS", "d^-1^")` (expected value and 95% highest density credible interval).
The expected value and 95% highest density credible intervals (95% HDCI) for the remaining coefficients are
in Table X.

## Tables

The mean and standard deviation of the data.

```{r, echo = FALSE}
cnames = c("Temperature", "Mean", "Std. Dev.") 
cap = "The mean and standard deviation of the data."
X %>% select(temperature, m, sd) %>% 
  knitr::kable(col.names = cnames,
               caption = cap)
```


The mean and 95% highest density credible intervals (HDCI) of the model coefficients.

```{r, echo = FALSE}
cnames = c("Coefficient", "Value", "95% Lower HDCI", "95% Upper HDCI")
cap = "The model coefficients and 95% highest density credible intervals."
datatable %>% select(key, value, .lower, .upper) %>% 
  mutate(key = if_else(str_detect(key, "CT"), "Kopt", key),
         key = if_else(str_detect(key, "PS"), "ymax", key)) %>% 
  knitr::kable(col.names = cnames, 
               caption = cap)
```

## Additional References

Paul-Christian Bürkner (2018). Advanced Bayesian Multilevel Modeling
  with the R Package brms. The R Journal, 10(1), 395-411.
  doi:10.32614/RJ-2018-017


R Core Team (2020). R: A language and environment for statistical
  computing. R Foundation for Statistical Computing, Vienna, Austria.
  URL https://www.R-project.org/.
  
  
Stan Development Team (2020). RStan: the R interface to Stan. R
  package version 2.21.3. http://mc-stan.org/.


