---
title: "Figure02"
author: "Greg Nishihara"
date: "12/8/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

For the details of the model see Figure04.docx and Figure04.Rmd.

## Run R

```{r, eval = FALSE, message=FALSE, warning=FALSE}
source("Figure02.R")
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
source("Figure02.R", echo = FALSE, print = FALSE, verbose = FALSE)
```

## The figure

The filenames of the image are `r str_replace(filename, "tex", "pdf")` and `r str_replace(filename, "tex", "png")`.

```{r, fig.cap=CAP, out.width="50%"}
CAP = "The response of (A) net photosynthesis, (B) gross photosynthesis, and (C) dark respiration rates against a range of water temperatures.
The solid lines indicate the expected value of the model and the symbols indicate the data. The shaded regions in (A) and (B) indicate 95% prediction interval of the data, however for (C) it is a 95% prediction interval of the model."

knitr::include_graphics(str_replace(filename, "tex", "png"))
```


```{r, echo = FALSE}
D = data %>% 
  group_by(temperature) %>% 
  summarise(m = mean(dark),
            sd =  sd(dark),
            se =  sd(dark) / sqrt(length(dark) -1)) %>% ungroup()
L = data %>% 
  group_by(temperature) %>% 
  summarise(m = mean(light),
            sd =  sd(light),
            se =  sd(light) / sqrt(length(light) -1)) %>% ungroup()

gen = function(x,y) {
  x = x %>% filter(temperature == y)
  S = "μg O~2~ g~ww~^-1^ min^-1^"
  sprintf("%2.1f ± %2.1f, %s", 
          x$m, x$sd, S)
}

gen2 = function(x,y, s = NULL) {
  w = x %>% 
    filter(str_detect(key, y))
  if(is.null(s)) {
    sprintf("%2.1f (%2.1f to %2.1f)", w$value, w$.lower, w$.upper)
  } else {
    sprintf("%2.1f (%2.1f to %2.1f) %s", w$value, w$.lower, w$.upper, s)
  }
}

gen3 = function(x,y, s = NULL) {
  w = x %>% 
    filter(str_detect(key, y))
  if(is.null(s)) {
    sprintf("%2.1f (%2.1f to %2.1f)", w$value, w$.lower, w$.upper)
  } else {
    sprintf("%2.1f (%2.1f to %2.1f) %s", w$value, w$.lower, w$.upper, s)
  }
}

datatable = tidy_draws(sout) %>% 
  select(PS, HA, ET, KT, EA, RD) %>% 
  mutate(HD = HA * ET,
         KT = KT - 273.15) %>% 
  select(-ET) %>% 
  gather() %>% 
  group_by(key) %>% 
  mean_hdci()
```


## Results

The mean net photosynthesis rates (Table X) ranged from `gen(L, 8)` at 8°C to `gen(L, 28)` at 28°C (mean ± standard deviation) and the mean darak respiration rates ranged from `gen(D,8)` at 8°C to `gen(D, 32)` at 32°C (Table Y).

The model analysis indicated that peak gross photosynthesis rate occurred at `r gen2(datatable, "KT", "°C")` and was `r gen3(datatable, "PS", "μg O~2~ g~ww~^-1^ min^-1^")` (Table Z). The dark respiration rate at 24°C (R~24~) was `r gen3(datatable, "RD", "μg O~2~ g~ww~^-1^ min^-1^")`


## Tables

```{r, echo = FALSE}
cnames = c("Temperature", "Mean", "Std. Dev.") 
cap = "Table X. The mean and standard deviation of the measured net photosynthesis rates."

L %>% 
  select(temperature, m, sd) %>% 
  knitr::kable(col.names = cnames, caption = cap,
               format = "pipe",
               digits = c(2,3,3))
```

```{r, echo = FALSE}
cnames = c("Temperature", "Mean", "Std. Dev.") 
cap = "Table Y. The mean and standard deviation of the measured dark respiration rates."

D %>% 
  select(temperature, m, sd) %>% 
  knitr::kable(col.names = cnames, caption = cap,
               format = "pipe",
               digits = c(2,3,3))
```


```{r, echo = FALSE}
cnames = c("Coefficient", "Value", 
           "95% Lower HDCI", "95% Upper HDCI")
cap = "Table Z. The model coefficients and 95% highest density credible intervals. Note that K~opt~ is given in °C."

datatable %>% select(key, value, .lower, .upper) %>% 
  mutate(key = factor(key,
                      levels = c("PS", "KT", "HA", "HD", "RD", "EA"),
                      labels = c("PS", "KT", "HA", "HD", "RD", "EA"))) %>% 
  arrange(key) %>% 
  mutate(key = as.character(key)) %>% 
  mutate(value = case_when(
    str_detect(key, "PS|RD")  ~ format(value, digits = 2),
    str_detect(key, "H[AD]|EA") ~ format(value, digits = 0),
    TRUE ~ format(value, digits = 2)
  )) %>%
  mutate(.lower = case_when(
    str_detect(key, "PS|RD")  ~ format(.lower, digits = 2),
    str_detect(key, "H[AD]|EA") ~ format(.lower, digits = 0),
    TRUE                     ~ format(.lower, digits = 2)
  )) %>%
  mutate(.upper = case_when(
    str_detect(key, "PS|RD")  ~ format(.upper, digits = 2),
    str_detect(key, "H[AD]|EA") ~ format(.upper, digits = 0),
    TRUE                     ~ format(.upper, digits = 2)
  )) %>%
  mutate(key = recode(key,
                      PS = "P~max~",
                      KT = "K~opt~",
                      HA = "H~a~",
                      HD = "H~d~",
                      RD = "R~24~",
                      EA = "E~a~")) %>% 
  knitr::kable(col.names = cnames, 
               caption = cap,
               format = "pipe",
               align = "lrrr")
```

## Additional References

Paul-Christian Bürkner (2018). Advanced Bayesian Multilevel Modeling
  with the R Package brms. The R Journal, 10(1), 395-411.
  doi:10.32614/RJ-2018-017


R Core Team (2020). R: A language and environment for statistical
  computing. R Foundation for Statistical Computing, Vienna, Austria.
  URL https://www.R-project.org/.
  
  
Stan Development Team (2020). RStan: the R interface to Stan. R
  package version 2.21.3. http://mc-stan.org/.


