---
title: "Figure01"
author: "Greg Nishihara"
date: "12/8/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

For the details of the model see Figure01.docx and Figure01.Rmd.

## Model

$$
P_{net} = P_{max}\left(1-\exp\left(\frac{-\alpha}{P_{max}}E\right)\right)-R_d
$$

## Run R

```{r, eval = FALSE, message=FALSE, warning=FALSE}
source("Figure01.R")
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
source("Figure01.R", echo = FALSE, print = FALSE, verbose = FALSE)
```

## The figure

The filenames of the image are `r str_replace(filename, "tex", "pdf")` and `r str_replace(filename, "tex", "png")`.

```{r, fig.cap=CAP, out.width="50%"}
CAP = "The response of the net photosynthesis rate to irradiance measured at (A) 12°C, (B) 20°C, and (C) 28°C. The solid line indicates the model and the symbols indicate the data.
The shaded region indicates the 95% prediction interval of the data."

knitr::include_graphics(str_replace(filename, "tex", "png"))
```


```{r, echo = FALSE}
X = data %>% 
  unnest(data) %>% 
  group_by(temperature,light) %>% 
  summarise(m = mean(rate),
            sd =  sd(rate),
            se =  sd(rate) / sqrt(length(rate) -1)) %>% ungroup()

gen = function(x,y,z, s = NULL) {
  x = x %>% filter(light == y , temperature == z) %>% print()
  if(is.null(s)) {
    sprintf("%2.1f ± %2.1f", x$m, x$sd)
  } else {
    sprintf("%2.1f ± %2.1f %s", x$m, x$sd, s)
  }
}

gen2 = function(x,y,z, s = NULL) {
  w = x %>% 
    filter(key == y , temperature == z)
  if(is.null(s)) {
    sprintf("%2.1f (%2.1f to %2.1f)", w$value, w$.lower, w$.upper)
  } else {
    sprintf("%2.1f (%2.1f to %2.1f) %s", w$value, w$.lower, w$.upper, s)
  }
}

gen3 = function(x,y,z, s = NULL) {
  w = x %>% 
    filter(light == y , temperature == z)
  if(is.null(s)) {
    sprintf("%2.3f (%2.3f to %2.3f)", w$value, w$.lower, w$.upper)
  } else {
    sprintf("%2.3f (%2.3f to %2.3f) %s", w$value, w$.lower, w$.upper, s)
  }
}

datatable = bout %>% mutate(params = map(bout, function(x) {
  x %>% fixef(summary = F) %>% 
    as_tibble() %>% 
    select(PM = PM_Intercept,
           AL = AL_Intercept,
           RD = RD_Intercept) %>% 
    gather() %>% 
    group_by(key) %>% 
    mean_hdci()
})) %>% 
  select(temperature, params) %>% 
  unnest(params)

```


## Results

The net photosynthesis rates responded similarly to irradiance (Fig. x) and the mean values ranged from 
`r gen(X, 0, 12, "μg O~2~ g~ww~^-1^ min^-1^")` to `r gen(X, 1000, 12, "μg O~2~ g~ww~^-1^ min^-1^")` at 12 °C, 
`r gen(X, 0, 20, "μg O~2~ g~ww~^-1^ min^-1^")` to `r gen(X, 1000, 20, "μg O~2~ g~ww~^-1^ min^-1^")` at 20 °C, and 
`r gen(X, 0, 27, "μg O~2~ g~ww~^-1^ min^-1^")` to `r gen(X, 1000, 28, "μg O~2~ g~ww~^-1^ min^-1^")` at 28 °C (Table X).

The model analysis indicated that the maximum photosynthesis rate (P~max~) increased from 
`r gen2(datatable, "PM", 12, "μg O~2~ g~ww~^-1^ min^-1^")` at 12°C to 
`r gen2(datatable, "PM", 28, "μg O~2~ g~ww~^-1^ min^-1^")` at 28°C and the dark respiration rate (R~d~) of 
`r gen2(datatable, "RD", 28, "μg O~2~ g~ww~^-1^ min^-1^")` was also higher at 28°C (Table Y).


## Tables

```{r, echo = FALSE}
cnames = c("Temperature", "Irradiance", "Mean", "Std. Dev.") 
cap = "Table X. The mean and standard deviation of the data."

X %>% 
  select(temperature, light, m, sd) %>% 
  knitr::kable(col.names = cnames, caption = cap,
               format = "pipe",
               digits = c(0,0,1,1))
```

```{r, echo = FALSE}
cnames = c("Coefficient", "Temperature", "Value", 
           "95% Lower HDCI", "95% Upper HDCI")
cap = "Table Y. The model coefficients and 95% highest density credible intervals."

datatable %>% select(temperature, key, value, .lower, .upper) %>% 
  relocate(key, .before = temperature) %>% arrange(key) %>% 
  mutate(value = case_when(
    str_detect(key, "PM|RD")  ~ format(value, digits = 1),
    TRUE ~ format(value, digits = 2)
  )) %>%
  mutate(.lower = case_when(
    str_detect(key, "PM|RD")  ~ format(.lower, digits = 1),
    TRUE                     ~ format(.lower, digits = 2)
  )) %>%
  mutate(.upper = case_when(
    str_detect(key, "PM|RD") ~ format(.upper, digits = 1),
    TRUE                     ~ format(.upper, digits = 2)
  )) %>%
  knitr::kable(col.names = cnames, 
               caption = cap,
               format = "pipe",
               align = "lrrrr")
```

## Additional References

Paul-Christian Bürkner (2018). Advanced Bayesian Multilevel Modeling
  with the R Package brms. The R Journal, 10(1), 395-411.
  doi:10.32614/RJ-2018-017


R Core Team (2020). R: A language and environment for statistical
  computing. R Foundation for Statistical Computing, Vienna, Austria.
  URL https://www.R-project.org/.
  
  
Stan Development Team (2020). RStan: the R interface to Stan. R
  package version 2.21.3. http://mc-stan.org/.


