---
title: "Figure03"
author: "Greg Nishihara"
date: "12/8/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

For the details of the model see Figure04.docx and Figure04.Rmd.

## Run R

```{r, eval = FALSE, message=FALSE, warning=FALSE}
source("Figure03.R")
```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
source("Figure03.R", echo = FALSE, print = FALSE, verbose = FALSE)
```

## The figure

The filenames of the image are `r str_replace(filename, "tex", "pdf")` and `r str_replace(filename, "tex", "png")`.

```{r, fig.cap=CAP, out.width="50%"}
CAP = "The response of effective quantum yield to temperature. The solid line indicates the expected value calculated from the model and
the shaded region indicates the 95% prediction interval of the model. Data are indicated by symbols."

knitr::include_graphics(str_replace(filename, "tex", "png"))
```


```{r, echo = FALSE}
X = data %>% 
  unnest(data) %>% 
  group_by(experiment, temperature) %>% 
  summarise(m = mean(yield),
            sd =  sd(yield),
            se =  sd(yield) / sqrt(length(yield) -1)) %>% ungroup()

gen = function(x,y,z, s = NULL) {
  x = x %>% filter(str_detect(experiment, as.character(z)), temperature == y) %>% print()
  if(is.null(s)) {
    sprintf("%2.3f ± %2.3f", x$m, x$sd)
  } else {
    sprintf("%2.3f ± %2.3f %s", x$m, x$sd, s)
  }
}

gen2 = function(x,y,z, s = NULL) {
  w = x %>% 
    filter(str_detect(experiment, as.character(z)), 
           str_detect(key, y))
  if(is.null(s)) {
    sprintf("%2.1f (%2.1f to %2.1f)", w$value, w$.lower, w$.upper)
  } else {
    sprintf("%2.1f (%2.1f to %2.1f) %s", w$value, w$.lower, w$.upper, s)
  }
}

gen3 = function(x,y,z, s = NULL) {
  w = x %>% 
    filter(str_detect(experiment, as.character(z)), 
           str_detect(key, y))
  if(is.null(s)) {
    sprintf("%2.3f (%2.3f to %2.3f)", w$value, w$.lower, w$.upper)
  } else {
    sprintf("%2.3f (%2.3f to %2.3f) %s", w$value, w$.lower, w$.upper, s)
  }
}

datatable = bout %>% mutate(params = map(bout, function(x) {
  x %>% fixef(summary = F) %>% 
    as_tibble() %>% 
    mutate(HD_Intercept = HA_Intercept * ET_Intercept,
           CT_Intercept = KT_Intercept - 273.15) %>% 
    select(CT = CT_Intercept,
           HA = HA_Intercept,
           HD = HD_Intercept,
           PS = PS_Intercept,
           ZI0 = zi_Intercept,
           ZI1 = zi_temperature) %>% 
    gather() %>% 
    group_by(key) %>% 
    mean_hdci()
})) %>% 
  select(experiment, params) %>% 
  unnest(params)

```


## Results

The effective quantum yields for the 24, 48, 72, and 96 hour exposure experiment responded similarly to temperature (Fig. x) and the mean values of the measured quantum yield ranged from 0 (undetectable) to 0.448 (Table x).

The model analysis indicated that peak effective quantum yield of the model occurred at `r gen2(datatable, "CT", 24, "°C")` for the 24 hour exposure experiment and increased to `r gen3(datatable, "PS", 24)`for the 72 hour exposure experiment (Table y). 
The peak effective quantum yield was also highest for the 72 hour experiment (Table y) and was `r gen3(datatable, "PS", 72)`.


## Tables

The mean and standard deviation of the data.

```{r, echo = FALSE}
cnames = c("Experiment", "Temperature", "Mean", "Std. Dev.") 
cap = "The mean and standard deviation of the data."

X %>% 
  select(experiment, temperature, m, sd) %>% 
  knitr::kable(col.names = cnames, caption = cap,
               format = "pipe",
               digits = c(NA,0,3,3))
```

The mean and 95% highest density credible intervals (HDCI) of the model coefficients.

```{r, echo = FALSE}
cnames = c("Coefficient", "Exposure", "Value", 
           "95% Lower HDCI", "95% Upper HDCI")
cap = "The model coefficients and 95% highest density credible intervals."

datatable %>% select(experiment, key, value, .lower, .upper) %>% 
  relocate(key, .before = experiment) %>% arrange(key) %>% 
  filter(!str_detect(key, "ZI")) %>% 
  mutate(key = if_else(str_detect(key, "CT"), "Kopt", key),
         key = if_else(str_detect(key, "PS"), "ymax", key)) %>% 
  mutate(value = case_when(
    str_detect(key, "ymax")  ~ format(value, digits = 3),
    str_detect(key, "H[AD]") ~ format(value, digits = 0),
    TRUE ~ format(value, digits = 1)
  )) %>%
  mutate(.lower = case_when(
    str_detect(key, "ymax")  ~ format(.lower, digits = 3),
    str_detect(key, "H[AD]") ~ format(.lower, digits = 0),
    TRUE                     ~ format(.lower, digits = 1)
  )) %>%
  mutate(.upper = case_when(
    str_detect(key, "ymax")  ~ format(.upper, digits = 3),
    str_detect(key, "H[AD]") ~ format(.upper, digits = 0),
    TRUE                     ~ format(.upper, digits = 1)
  )) %>%
  knitr::kable(col.names = cnames, 
               caption = cap,
               format = "pipe",
               align = "llrr")
```

## Additional References

Paul-Christian Bürkner (2018). Advanced Bayesian Multilevel Modeling
  with the R Package brms. The R Journal, 10(1), 395-411.
  doi:10.32614/RJ-2018-017


R Core Team (2020). R: A language and environment for statistical
  computing. R Foundation for Statistical Computing, Vienna, Austria.
  URL https://www.R-project.org/.
  
  
Stan Development Team (2020). RStan: the R interface to Stan. R
  package version 2.21.3. http://mc-stan.org/.


